---
title: "Analysing accuracy data with GLMM models: Sneak peek"
author: "Maria Korochkina"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: cerulean
fontsize: 16pt
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Load required packages

```{r, results = "hide"}
rm(list=ls())

library("openxlsx")
library("Rmisc")
library("tidyverse")
library("lme4")
library("car")
library("MASS")
library("scales")
library("lmerTest")
library("sjmisc")
library("sjPlot")
library("ggsignif")
library("RColorBrewer")
library("rms")
library("broom.mixed")
```

# Load data

Data that we will be using today is available [here](https://github.com/mariakna/MQ-eResearchTraning--G-LMEmodels). 

Download the file *nwl.xlsx*, save it in a directory of your choice, make this directory your working directory by using the command `setwd()` and load the file as shown below:

```{r}
data <- read.xlsx("nwl.xlsx", sheet = 1)
```

## Data description

This file contains data from a word learning task. German native speakers learned new names for familiar concepts (e.g., *Marp* for cat), simulating word learning in a foreign language. As part of the learning procedure, they were asked to name the pictures of the familiar concepts (e.g., cat) using the novel names (e.g., *Marp*). The words were taught in two conditions, categorically related (*CRel*) and unrelated (*UnRel*). We wish to know whether, averaged across the first 8 naming attempts, the participants were more accurate in the unrelated condition.

* `Subj`: Participant ID (N = 60)
* `Session`: there were 2 sessions, with 8 naming attempts in Session 1 and 4 naming attempts in Session 2
* `NamingAttempts`: factor with 1-12 levels
* `LC`: factor with 2 levels, `CRel` and `UnRel`
* `Response`: participant's response
* `Accuracy`: a factor with 2 levels, `0` = incorrect responses, `1` = correct responses
* `RT`: response times

Restrict the dataset to the first 8 naming attempts:

```{r}
data2 <- data %>%
  filter(Session == "1")
```

Adjust factor levels for the independent variable and random terms:

```{r}
data2$LC <- factor(data2$LC)
data2$Subj <- factor(data2$Subj)
data2$NovelName <- factor(data2$NovelName)
```